### 2011-03-20 extra/sliver_pldi11/preliminaries.tex

Our pruning technique works on Datalog, a general language which can be used to
express static analyses declaratively \cite{Whaley2007,bravenboer}.  Normally,
these analyses are encoded by one monolithic Datalog program which computes an
abstract answer to a query.  For us, it will be convenient to consider the
Datalog program, which computes the concrete\footnote{We refer to this computation as ``concrete''
to contrast with abstract computation we will consider later,
but note that this ``concrete'' computation
could already contain some level of abstraction.
For example, the Datalog program might correspond to $\infty$-object-sensitivity
without abstraction and $k$-object-sensitivity with abstraction.
}
answer to a query, as distinct
from the abstraction, which is applied on the Datalog program to compute an
abstract answer.  This separation allow us to make theoretical statements
comparing the behavior of the same Datalog program across different
abstractions.

@@

\begin{figure}
\[
\arraycolsep=3.5pt
\begin{array}{llllllll}
\{\vec{0}\}    &            &              &            & \{\vec{1}\} \\
\{\vec{00}\}   &            & \{\vec{01}\} &            & \{\vec{10}\} &            & \{\vec{11}\} \\
\vec{000}*     & \vec{001}* & \vec{010}*   & \vec{011}* & \vec{100}*   & \vec{101}* & \vec{110}* & \vec{111}*
\end{array}
\]
\caption{\label{fig:repeatingExample} For the $k$-limited abstraction
with $\dom = \{ 0, 1 \}$ and $k = 3$, the equivalence classes defined by $\klimabs_k$.
}
\end{figure}

>>>>

Our pruning technique works on Datalog, a general language which can be used to
express static analyses declaratively \cite{Whaley2007,bravenboer}.  Normally,
these analyses and their underlying abstractions are encoded by one monolithic Datalog program
which evaluates a query abstractly.
For us, it will be convenient to consider the
Datalog program, which evaluates a query concretely\footnote{We refer to this computation as ``concrete''
to contrast with abstract computation we will consider later,
but note that this ``concrete'' computation
could already contain some level of abstraction.
For example, the Datalog program might correspond to $\infty$-object-sensitivity
without abstraction and $k$-object-sensitivity with abstraction.
}, as distinct
from the abstraction, which is defined as a transformation on the input to
the Datalog program, and makes it evaluate the query abstractly.  This separation
allows us to make theoretical statements
comparing the behavior of the same Datalog program across different
abstractions.

@@

\begin{figure}
\[
\arraycolsep=3.5pt
\begin{array}{llllllll}
\{\vec{0}\}    &            &              &            & \{\vec{1}\} \\
\{\vec{00}\}   &            & \{\vec{01}\} &            & \{\vec{10}\} &            & \{\vec{11}\} \\
\vec{000}*     & \vec{001}* & \vec{010}*   & \vec{011}* & \vec{100}*   & \vec{101}* & \vec{110}* & \vec{111}*
\end{array}
\]
\caption{\label{fig:repeatingExample}
The equivalence classes defined by the $k$-limited abstraction $\klimabs_k$
with $\dom = \{ 0, 1 \}$ and $k = 3$,
In other words, $\klimabs_k$ maps each chain $c \in \dom^*$ to one of the 14 abstract values above.
}
\end{figure}
